---
title: "Respirometry - assemble final values from LoLin outputs"
author: "Samuel Gurr"
date: "October 29, 2018"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
##Install and load packages
library(dplyr)
library(plyr)
library(ggplot2)
library(ggpubr)
library(Rmisc)
library(nlme)
library(lme4)
library(ggplot2) 
library(lme4)
library(ggpubr)
library(nlme)
library(plotrix)
library(lsmeans)
library(gridExtra)
library(seacarb) 
library(reshape) 
library(plotrix) 
library(ggplot2) 
library(plyr)
library(gridExtra)
library(multcompView)
library(lsmeans)
library(knitr)
library(kableExtra)
#set working directory--------------------------------------------------------------------------------------------------
setwd("C:/Users/samjg/Documents/Notebook/data/Geoduck_Conditioning/RAnalysis/") #set working

#Load Respiraiton Data
resp<-read.csv("Data/All_resp_calc_and_standardized.csv", header=T, sep=",", na.string="NA", as.is=T) 
names(resp) # view the names of the data
# seperate into experiment 1 and 2 for the 10-day and 6-day OA exposure
resp_EXP1 <- subset(resp, EXP.numb=="EXP1") #initial 10-day trial, subset entire dataset resp by column nsame "Exp.num" == Exp1
resp_EXP2 <- subset(resp, EXP.numb=="EXP2") #second 6-day trial, subset entire dataset resp by column nsame "Exp.num" == Exp2
resp_EXP2.0 <- subset(resp, EXP.numb=="EXP2") # same under a diff name (read why on next comment)
resp_EXP2.0 <-subset(resp_EXP2.0, Day!=0) #eliminate Day0 of the second exposure for graph on cumulative exposure to OA 

newdata_resp_EXP1_ALL <- data.frame(resp_EXP1$Date, resp_EXP1[,c(1:10)])
newdata_resp_EXP1_ALL_1 <-newdata_resp_EXP1_ALL[c(57,52,3,6,17,2,1,76,50,96,31,5,29,70,72,68,56,94), ]

```

## Exposure 1 (10-day OA): SMR and respirometry

plot all automated outputs to the "reference"

Reference = each value saved individually based on visual criteria of LoLin plots defatult at alpha 0.2, no truncation, and Lpc

Automated ouputs = looped the LoLin function for nine pairs of constants at alpha = 0.2, 0.4 and 0.6 for three levels of truncation of 30 minute trials (no truncation, 10-20mins, 10-25 mins) - aways target Lpc. 

Below you can see that alpha 0.2 and alpha 0.4 with no truncation are strongly correlated to the reference 

```{r , echo=FALSE}
par(mfrow=c(2,2))
plot(resp_EXP1[,1],resp_EXP1[,2], main= "Ref vs. alpha0.2_all")#Adjusted R-squared:  0.4987 

plot(resp_EXP1[,1],resp_EXP1[,3], main= "Ref vs. alpha0.2_min10.20")#Adjusted R-squared:  0.2892

plot(resp_EXP1[,1],resp_EXP1[,4], main= "Ref vs. alpha0.2_min10.25")#Adjusted R-squared:  0.1674

plot(resp_EXP1[,1],resp_EXP1[,5], main= "Ref vs. alpha0.4_all")#Adjusted R-squared:  0.3905

plot(resp_EXP1[,1],resp_EXP1[,6], main= "Ref vs. alpha0.4_min10.20")#Adjusted R-squared:  0.2589 

plot(resp_EXP1[,1],resp_EXP1[,7], main= "Ref vs. alpha0.4_min10.25")#Adjusted R-squared:  0.315 

plot(resp_EXP1[,1],resp_EXP1[,8], main= "Ref vs. alpha0.6_all")#Adjusted R-squared:  0.4947 

plot(resp_EXP1[,1],resp_EXP1[,9], main= "Ref vs. alpha0.6_min10.20")#Adjusted R-squared:  0.4037 

plot(resp_EXP1[,1],resp_EXP1[,10], main= "Ref vs. alpha0.6_min10.25")#Adjusted R-squared:  0.4409 


```

## Create an final dataset (LOESS curve, linear regression, merge data)
1) Determine that alpha = 0.4 no truncation has LEAST number of points outside of the LOESS curve to the reference 

-  ID points outside of the LOESS CI interval

RESULT: 18 points outside of loess 

```{r , echo=FALSE}
# Below used alpha = 0.4, no truncation for automated ouput because of the Least number of respiration values outside of Loess CI with Reference
ggplot(resp_EXP1, aes(x = resp_EXP1[,1], y = resp_EXP1[,5])) +
  geom_point() +
  geom_smooth(method = 'loess') +
  geom_text(aes(label = resp_EXP1$ID), position = position_nudge(y = -0.01))

```

2) call these 18 values for each column (automated LoLin ouput) into a new dataframe

Run linear regressions to the reference 

RESULT: Alpha = 0.6 10-25 minute (truncation) or 'respEX1_..[,10]' has strongest correlation to reference (r = 0.7235) 

```{r , echo=FALSE}
par(mfrow=c(2,2))
plot(newdata_resp_EXP1_ALL_1[,2],newdata_resp_EXP1_ALL_1[,3])#Adjusted R-squared: 0.5145 

plot(newdata_resp_EXP1_ALL_1[,2],newdata_resp_EXP1_ALL_1[,4])#Adjusted R-squared:  0.6196 

plot(newdata_resp_EXP1_ALL_1[,2],newdata_resp_EXP1_ALL_1[,5])#  0.07991

plot(newdata_resp_EXP1_ALL_1[,2],newdata_resp_EXP1_ALL_1[,6])# 0.0618 

plot(newdata_resp_EXP1_ALL_1[,2],newdata_resp_EXP1_ALL_1[,7])#0.3223 

plot(newdata_resp_EXP1_ALL_1[,2],newdata_resp_EXP1_ALL_1[,8])#0.205 

plot(newdata_resp_EXP1_ALL_1[,2],newdata_resp_EXP1_ALL_1[,9])#0.2356 

plot(newdata_resp_EXP1_ALL_1[,2],newdata_resp_EXP1_ALL_1[,10]) # alpha = 0.6 10-20 min# 0.7235 

plot(newdata_resp_EXP1_ALL_1[,2],newdata_resp_EXP1_ALL_1[,11])#  0.3334 

```

3) Merge with alpha 0.4 no truncation to create final column. Plot with reference.


```{r , echo=FALSE}
#create a new column 
resp_EXP1$FINALresp <- resp_EXP1$LpcResp_alpha0.4_all.csv # base alpha 0.4, no truncation
resp_EXP1$FINALresp[c(57,52,3,6,17,2,1,76,50,96,31,5,29,70,72,68,56,94)] <- resp_EXP1$LpcResp_alpha0.6_min10.20.csv[c(57,52,3,6,17,2,1,76,50,96,31,5,29,70,72,68,56,94)] #inserted new rows from alpha = 0.6 10-20 min for points outside loess curve
# test correlation of this new column with the Ref
plot(resp_EXP1$Resp_individually_all.csv,resp_EXP1$FINALresp, main= "Ref vs. FINALresp") # plot the relationship
summary(lm(resp_EXP1[,1]~resp_EXP1$FINALresp)) # summarize linear model - Multiple R-squared:  0.8784,	Adjusted R-squared:  0.8771 
ggplot(resp_EXP1, aes(x = resp_EXP1[,1], y = resp_EXP1$FINALresp)) +
  geom_point() +
  geom_smooth(method = 'loess') +
  geom_text(aes(label = resp_EXP1$ID), position = position_nudge(y = -0.01)) # ggplot with loess CI
  
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
